Accounting for Fiber Collisions in the Galaxy Power Spectrum Measurements

### 2015-12-17 fc_paper/fc_paper.tex
Some structural edits to the paper. Need to work on content.

%define general packages
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{footnote}
\usepackage{setspace}
\usepackage{courier}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% fiber collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Accounting for Fiber Collisions} \label{sec:fc_corr}
%Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:fc_pk} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance. In order to correct for this effect, in Section \ref{sec:dlospeak} we present an improved method to account for correlated fiber collided galaxies that uses the line-of-sight displacement between fiber collided pairs (Section \ref{sec:dlos}) and a shot-noise correction term in the power spectrum estimator that properly takes into account fiber collisions (Section \ref{sec:shotnoise}). In Section \ref{sec:fourier}, we present a complementary method that models the effect of fiber collisions on the power spectrum using an analytic estimate of the effect of fiber collisions on the 2PCF. 
\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs. The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}. We also plot the ratio of the sample variance to the true $\overline{P_\mathrm{true}(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) for comparison. Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:fc_pk}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Effects of Fiber Collision on the Power Spectrum 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nearest Angular Neighbor Method} \label{sec:fc_pk}
A common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}), hereafter NN method. For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor. This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 \arcsec$ for BOSS) are correlated with one another. In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one of the galaxies and placing it on top of the other does not significantly alter the clustering statistics. One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position. For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$. Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements.

% Not only quantify the effect of fiber collisions, but the break down of the NN method for P(k) at high k. 
To precisely quantify the effect of fiber collisions on the power spectrum, in Figure \ref{fig:fc_pk}, we compare $P_0(k)$ and $P_2(k)$ measured using the NN method for mock catalogs with fiber collisions to the $P_0(k)$ and $P_2(k)$ measurements for mock catalogs without fiber collisions. The $P_0(k)$ measurements are made using Eq. \ref{eq:roman_p0k} with a standard FKP shot noise ($N_0^{FKP}$) rather than $N_0$ from Eq. \ref{eq:roman_shotnoise}, which is effectively just the standard power spectrum estimator from \cite{Feldman:1994aa}. $P_2(k)$ measurements are made using Eq. \ref{eq:roman_p2k}. 
\begin{itemize}
	\item Description of Figure \ref{fig:fc_pk} focusing on the scales where the NN method breaks down and quantifying the residuals. 
\end{itemize}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute the $d_{\mathrm{LOS}}$ distributions. The $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above). We focus on the peak of the distribution $-20 \; \mathrm{Mpc} < d_\mathrm{LOS} < 20 \;\mathrm{Mpc}$ (discussed in \ref{sec:dlos}).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DLOSPEAK METHOD 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{First Method} \label{sec:dlospeak}
% LOS DISPLACEMENT %%%%
\subsubsection{Line-of-Sight Displacement of Fiber Collided Pairs} \label{sec:dlos}
It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments. Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and measure the fraction of pairs that are corrected and uncorrelated.

For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated. Redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$). So in a situation where only two galaxies are within the fiber collision angular scale, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies ($w_{\mathrm{fc}} = 2$), while the other has $w_\mathrm{fc} = 0$. Nonetheless, since we actually have redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better understand the effects of fiber collisions.

@@

After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor). All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak roughly contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}). For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber collided pairs without spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber collided pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.

@@

 \begin{table} 
 \caption{$d_{\mathrm{LOS}}$ Distribution Best-fit Parameters} \label{tab:mpfit}
 \begin{spacing}{1.5}
 \begin{center}
 \leavevmode
 \begin{tabular}{ccc} \hline \hline
catalog &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
LasDamas 	& 6.85	& 0.71 \\ 
QPM 		& 4.98	& 0.65 \\ 
Tiling Mock 	& 5.38	& 0.57 \\ 
BOSS DR12 	& 7.6		& 0.65 \\ \hline
\end{tabular} \par
\end{center}
\end{spacing}
%    \bigskip 
{\bf Notes}: Best-fit parameter $\sigma$ (Eq. \ref{eq:peak}) and peak fraction $f_{\mathrm{peak}}$ (Eq. \ref{eq:fpeak}) for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
\end{table}

@@

For the NN method to be entirely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case. By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales. Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as the NN correction does, placing the fiber collided galaxy at a displacement, sampled from the $d_{\mathrm{LOS}}$ distribution, apart from its nearest neighbor better accounts for the small scale in clustering measurements.

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_shotnoiseonly_comp.png}
\caption{The ratio of $\overline{P_\mathrm{SN}(k)}$ computed using the shot-noise correction term given by Eq. \ref{eq:fkp_shotnoise} (blue), Eq. \ref{eq:ourshot} (green), $P^\mathrm{B2014}_\mathrm{shot}$ (red), and $P^{\mathrm{GM2014}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs. We also plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ to compare with the sample variance ratio. $\overline{P_\mathrm{SN}(k)}$ computed using Eq. \ref{eq:fkp_shotnoise} shot-noise correction is identical to the NN method $\overline{P_\mathrm{corr}(k)}$ presented in Figure \ref{fig:peakonly} and as before significantly overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$. $\overline{P_\mathrm{SN}(k)}$ using $P^\mathrm{B2014}_\mathrm{shot}$ equivalently overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$. On the other hand $\overline{P_\mathrm{SN}(k)}$ computed using Eq. \ref{eq:ourshot} significantly underestimates the power spectrum at $k > 0.1 \; h/\mathrm{Mpc}$ with $\overline{P^\mathrm{Eq.15}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim -3 \%, -8 \%, \;\mathrm{and} -9$ for LasDamas, QPM, and Tiling Mock respectively. $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{GM2014}_\mathrm{shot}$ provides the best correction for fiber collisions ($\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim 2.5 \%$). However at these small scales, even for $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ the effect of fiber collisions is comparable to sample variance at $k \sim 0.3 \;h/\mathrm{Mpc}$. } \label{fig:shotnoise}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SHOT NOISE CORRECTION 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shot Noise Correction} \label{sec:shotnoise} 
Both the NN method and the $d_\mathrm{LOS}$-peak correction do not sufficiently account for the systematic effects of fiber collisions in the power spectrum. In this section we introduce the other part of our fiber collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator. By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber collided pairs.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakshotnoise_mpfit_comp.png} 
\caption{The ratio of $\overline{P(k)}$ computed using our fiber collision correction method presented in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs with nearest-neighbor fiber collision weights (red). We again plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ for comparison. $\overline{P_\mathrm{corr}}/\overline{P_\mathrm{true}}(k \sim 0.3 \; h/\mathrm{Mpc})-1 \sim 0.5\%$ for our fiber collision correction. This is significantly better than the correction methods of \cite{Anderson:2012aa}, \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} in Figure \ref{fig:shotnoise}. Moreover, for LasDamas and QPM, our correction method is able to correct for the effects of fiber collisions, significantly below the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ range, even at the smallest scales. }\label{fig:peaksn}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESULT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} \label{sec:results}
\subsection{fiber collision Correction Method} \label{sec:apply}
In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution. Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs. We now combine these two methods and present our fiber collision correction method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Goodness of fit
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Goodness-of-fit} \label{sec:litcomp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHI-SQUARED FIGURE 
\begin{figure*} 
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_chisquared_comparison.png} 
\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the LasDamas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogs. Equation \ref{eq:chi2} was used to compute the $\chi^2(k_\mathrm{max})$. }\label{fig:peaksnchi2}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHI-SQUARED FIGURE

>>>>

%define general packages
\usepackage{color}
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{footnote}
\usepackage{setspace}
\usepackage{courier}

\newcommand{\todo}[1]{{\bf \textcolor{red}{ #1}}}
%\newcommand\todo[1]{{\color{red}#1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% fiber collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber Collision Methods} \label{sec:fc_corr}
%Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:fc_pk} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance. In order to correct for this effect, in Section \ref{sec:dlospeak} we present an improved method to account for correlated fiber collided galaxies that uses the line-of-sight displacement between fiber collided pairs (Section \ref{sec:dlos}) and a shot-noise correction term in the power spectrum estimator that properly takes into account fiber collisions (Section \ref{sec:shotnoise}). In Section \ref{sec:fourier}, we present a complementary method that models the effect of fiber collisions on the power spectrum using an analytic estimate of the effect of fiber collisions on the 2PCF. 
\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs. The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}. We also plot the ratio of the sample variance to the true $\overline{P_\mathrm{true}(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) for comparison. Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:fc_pk}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Effects of Fiber Collision on the Power Spectrum 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nearest Angular Neighbor Method} \label{sec:fc_pk}
A common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}), hereafter NN method. For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor. This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 \arcsec$ for BOSS) are correlated with one another. In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one of the galaxies and placing it on top of the other does not significantly alter the clustering statistics. One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position. For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$. Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements.

% Not only quantify the effect of fiber collisions, but the break down of the NN method for P(k) at high k. 
To precisely quantify the effect of fiber collisions on the power spectrum, in Figure \ref{fig:fc_pk}, we compare $P_0(k)$ and $P_2(k)$ measured using the NN method for mock catalogs with fiber collisions to the $P_0(k)$ and $P_2(k)$ measurements for mock catalogs without fiber collisions. The $P_0(k)$ measurements are made using Eq. \ref{eq:roman_p0k} with a standard FKP shot noise ($N_0^{FKP}$) rather than $N_0$ from Eq. \ref{eq:roman_shotnoise}, which is effectively just the standard power spectrum estimator from \cite{Feldman:1994aa}. $P_2(k)$ measurements are made using Eq. \ref{eq:roman_p2k}. \todo{Description of Figure \ref{fig:fc_pk} focusing on the scales where the NN method breaks down and quantifying the residuals.}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{\todo{bin CMASS with wider bins}Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute the $d_{\mathrm{LOS}}$ distributions. The $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above). We focus on the peak of the distribution $-20 \; \mathrm{Mpc} < d_\mathrm{LOS} < 20 \;\mathrm{Mpc}$ (discussed in \ref{sec:dlos}).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DLOSPEAK METHOD 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{First Method} \label{sec:dlospeak}
\todo{Come up with better title for subsection}
% LOS DISPLACEMENT %%%%
\subsubsection{Line-of-Sight Displacement of Fiber Collided Pairs} \label{sec:dlos}
It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments. Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and measure the fraction of pairs that are correlated and uncorrelated.

For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated. Redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$). For example, in a situation where only two galaxies are within the fiber collision angular scale, the NN method assigns one galaxy (``the nearest neighbor") the fiber collision weight of both galaxies ($w_{\mathrm{fc}} = 2$), while the other has $w_\mathrm{fc} = 0$. Nonetheless, since we actually have redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better understand the effects of fiber collisions.

@@

After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for \todo{LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor)}. All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak roughly contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$. The entire range of the distribution is not displayed in Figure \ref{fig:d_los}. For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber collided pairs without spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber collided pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.

@@

 \begin{table} 
 \caption{$d_{\mathrm{LOS}}$ Distribution Best-fit Parameters} \label{tab:mpfit}
 \begin{spacing}{1.5}
 \begin{center}
 \leavevmode
 \begin{tabular}{ccc} \hline \hline
catalog &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
LasDamas 	& 6.85	& 0.71 \\ 
QPM 		& 4.98	& 0.65 \\ 
Tiling Mock 	& 5.38	& 0.57 \\ 
BOSS DR12 	& 7.6		& 0.65 \\ \hline
\end{tabular} \par
\end{center}
\end{spacing}
%    \bigskip 
{\bf Notes}: \todo{update this table} Best-fit parameter $\sigma$ (Eq. \ref{eq:peak}) and peak fraction $f_{\mathrm{peak}}$ (Eq. \ref{eq:fpeak}) for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
\smallskip
\end{table}

@@

For the NN method to be entirely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case. By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales. Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as the NN correction does, placing the fiber collided galaxy at a displacement, sampled from the $d_{\mathrm{LOS}}$ distribution, apart from its nearest neighbor better accounts for the small scale in clustering measurements. However,

@@

\todo{Instead of describing dLOS peak only, describe how "peak-assigned" galaxies are determined. Then transition to the shot noise correction term}.

In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution. Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs. We now combine these two methods and present our fiber collision correction method.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_shotnoiseonly_comp.png}
\caption{The ratio of $\overline{P_\mathrm{SN}(k)}$ computed using the shot-noise correction term given by Eq. \ref{eq:fkp_shotnoise} (blue), Eq. \ref{eq:ourshot} (green), $P^\mathrm{B2014}_\mathrm{shot}$ (red), and $P^{\mathrm{GM2014}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs. We also plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ to compare with the sample variance ratio. $\overline{P_\mathrm{SN}(k)}$ computed using Eq. \ref{eq:fkp_shotnoise} shot-noise correction is identical to the NN method $\overline{P_\mathrm{corr}(k)}$ presented in Figure \ref{fig:peakonly} and as before significantly overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$. $\overline{P_\mathrm{SN}(k)}$ using $P^\mathrm{B2014}_\mathrm{shot}$ equivalently overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$. On the other hand $\overline{P_\mathrm{SN}(k)}$ computed using Eq. \ref{eq:ourshot} significantly underestimates the power spectrum at $k > 0.1 \; h/\mathrm{Mpc}$ with $\overline{P^\mathrm{Eq.15}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim -3 \%, -8 \%, \;\mathrm{and} -9$ for LasDamas, QPM, and Tiling Mock respectively. $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{GM2014}_\mathrm{shot}$ provides the best correction for fiber collisions ($\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim 2.5 \%$). However at these small scales, even for $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ the effect of fiber collisions is comparable to sample variance at $k \sim 0.3 \;h/\mathrm{Mpc}$. } \label{fig:shotnoise}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SHOT NOISE CORRECTION 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shot Noise Correction} \label{sec:shotnoise} 
\todo{Discuss the different shot-noise correction considerations in the literature}
Both the NN method and the $d_\mathrm{LOS}$-peak correction do not sufficiently account for the systematic effects of fiber collisions in the power spectrum. In this section we introduce the other part of our fiber collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator. By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber collided pairs.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fourier Tophat Method 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Second Method} \ref{sec:fourier}
\begin{itemize}
\item \todo{Figure of 2PCF that demonstrates a pretty clear tophat} 
\item \todo{The ultimate equations for calculating the tophat convolution}
\item \todo{Polynomials estimations of the integral?}
\item \todo{Figures of the fourier tophat method in action}
\end{itemize}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakshotnoise_mpfit_comp.png} 
\caption{The ratio of $\overline{P(k)}$ computed using our fiber collision correction method presented in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs with nearest-neighbor fiber collision weights (red). We again plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ for comparison. $\overline{P_\mathrm{corr}}/\overline{P_\mathrm{true}}(k \sim 0.3 \; h/\mathrm{Mpc})-1 \sim 0.5\%$ for our fiber collision correction. This is significantly better than the correction methods of \cite{Anderson:2012aa}, \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} in Figure \ref{fig:shotnoise}. Moreover, for LasDamas and QPM, our correction method is able to correct for the effects of fiber collisions, significantly below the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ range, even at the smallest scales. }\label{fig:peaksn}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESULT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} \label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Goodness of fit
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Goodness-of-fit} \label{sec:litcomp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHI-SQUARED FIGURE 
\begin{figure*} 
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_chisquared_comparison.png} 
\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the LasDamas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogs. Equation \ref{eq:chi2} was used to compute the $\chi^2(k_\mathrm{max})$. }\label{fig:peaksnchi2}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHI-SQUARED FIGURE
